---
title: "Demographics-Foster_care"
author: "Julie Rebstock and JaiDa Robinson"
date: "6/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Whole Population of Loudoun County 
[source](https://www.loudoun.gov/DocumentCenter/View/122720/LEP-PLAN-CULTURAL-DEMOGRAPHICS---Updated-May-2021?bidId=)

```{r}
library(ggplot2)
library(readxl)
```


**Race** 

```{r}

white <- c(256903, 60.9) 
black <- c(31925, 7.6) 
indian <- c(1303, .3) 
asian <- c(85942, 20.4) 
native_hawaiian <- c(351, .1) 
other <- c(24568, 5.8)  
two_more <- c(20644 , 4.9) 
total <- c(421636 , 100) 
table <- data.frame(rbind(white, black, indian, asian, native_hawaiian, other, two_more, total)) 
  
colnames(table) <- c("Population", "Percent")

pie(table$Percent[1:7],  labels = rownames(table), main= "Races of Loudoun County")


```


**Age and Sex ** 
[source](https://www.livehealthyloudoun.org/demographicdata?id=2924&sectionId=942)

```{r}

# age <- read.csv("/Users/julierebstock/Desktop/Virginia Tech/DSPG 2021/Loudoun County/Demographics/Population_by_Age_Group_County_Loudoun.csv")
# colnames(age) <- c("Age Group", "Percent")
# 
# barplot(age$Percent, main = "Age in Loudoun County", xlab = "Age Groups", ylab = "Percentage",names.arg = age$`Age Group`,las =2,col = "blue")
# 
# male <- c(211323,	49.50)
# female <- c(215631,	50.50)
# 
# sex <- data.frame(rbind(male, female)) 
# colnames(sex) <- c("Population", "Percent")
# sex$Group <- c("Male", "Female")
# 
# bp<- ggplot(sex, aes(x="", y=Percent, fill=Group))+
# geom_bar(width = 1, stat = "identity")
# 
# gender <- bp + coord_polar("y", start=0)
# gender

```



**Education by Gender**
[source](https://censusreporter.org/data/table/?table=B15002&primary_geo_id=05000US51107&geo_ids=05000US51107,04000US51,01000US)

```{r}
# education <- read_excel("/Users/julierebstock/Desktop/Virginia Tech/DSPG 2021/Loudoun County/Demographics/education /acs2019_1yr_B15002_01000US.xlsx")
# 
# education <- education[-c(1,2,3), c(1,6)]
# colnames(education) <- c("Schooling", "Total")
# 
# education_m <- education[c(2:17),]
# education_m
# 
# education_f <- education[-c(1:18),]
# education_f
# 
# education_percent <- 93.9
## need visualization 


```


**Household Income (2019)** 
[CSV](https://datausa.io/api/data?measure=Household%20Income,Household%20Income%20Moe&geo=05000US51107,01000US&drilldowns=Household%20Income%20Bucket)

```{r}

# household <- read_excel("/Users/julierebstock/Desktop/Virginia Tech/DSPG 2021/Loudoun County/Demographics/income/acs2019_1yr_B19001_01000US.xlsx") 
# 
# household_clean <- data.frame(household[1], household[6]) 
# household_clean <- household_clean[-c(1,2,3,4), ]
# colnames(household_clean) <- c("Income", "Value")
# 
# household_clean

```


**Homes/Household data** 
[CSV](https://data.census.gov/cedsci/profile?g=0500000US51107)


## Transitional Aged Youth (18-24) in Loudoun County 
[source](https://www.livehealthyloudoun.org/demographicdata?id=2924&sectionId=942)

```{r}
tays_pop <- 17352+ 20448 

tays_m <- 8837+10241
tays_f <- 8515+10207

## need visualization

```

**Race** 
[source](https://data.census.gov/cedsci/table?g=0500000US51107&tid=ACSDT1Y2019.B01001B)

```{r}

w <- 3182+6792+2857+6627
b <- 381+918+361+868
i <- 53+29
as <- 1365+507+1485+534
nh <- 54+25
o <- 392+521+288+137 
tw <- 329+989+535+621

w+b+i+as+nh+o+tw

## not accurate because its from 2019 and the total population is from 2021 

```



## Foster Care

Child Trends [Source](https://www.childtrends.org/wp-content/uploads/2017/11/SYPTFC-Virginia-Findings-from-a-National-Survey-and-Policy-Scan-11.29.17.pdf)

The AFCARS Report [Source](https://www.acf.hhs.gov/cb/report/afcars-report-27)

Virginia Department of Social Services [Source](https://www.dss.virginia.gov/geninfo/reports/children/fc.cgi)

```{r}
foster_care_2020 <- read_excel("01-Doc/Summaries/data/foster-care-2020-all.xlsx")
View(foster_care_2020)

```

```{r}
sex_df <- data.frame(foster_care_2020[c(2,4),])
colnames(sex_df) <- c("Gender", "Value")

pie(sex_df$Value, sex_df$Gender, main = "Gender of Foster Care Youth in Loudoun County")
    
```

```{r}

race <- data.frame(foster_care_2020[c(8,10,12,14,16,18),])
colnames(race) <- c("Race", "Value")
races <- c("Black", "White", "Indian", "Asian", "Hawaiian", "Multi") 
race_p <- data.frame(foster_care_2020[c(9,11,13,15,17,19),])
colnames(race_p) <- c("Race", "Percent")

r <- barplot(race$Value, xlab = "Races", ylab = "Values")
axis(1, at = r, labels=races, cex.axis=0.6)


eth <- foster_care_2020[22,]

fc_tays <- foster_care_2020[c(37,38),]

```


**Foster Care in the US** 
In the US 2019, 423,997 children were in the foster system with 251,359 newly entered children and 248,669 exiting. The average age of a child in foster care is 8.4 years old and males are the majority by 4%. For the Transitional Aged Youth (18-24), they only make up about 4% of the total foster care youth in the US. 44% of foster care youth are white and 23% were black. Similar to foster care statistics in Virginia alone, the average time in care is 19.6 months. According to *The AFCARS Report* in 2019, only 3,335 (1%) children who entered the foster care system were 18+ and it was most likely due to neglect. However, there were 20,465 (8%) youths 18+ who exited the system most likely due to aging out and emancipation. 


**Foster Care in Virginia** 
Based on the 2020 Foster Care Reports from *The Adoption and Foster Care Analysis and Reporting System*, there were 5,530 children in foster care in Virginia with the majority of them being ages 1-5 years old (23.5%) and second most children being ages 16-18 (20.7%). The average time they were in care was 18.85 months whether that was they were adopted, returned home, started living in Independent living, placed with relatives or aged out. 


**Foster Care Transitional Aged Youth in Virginia** 
Based on the table from *Supporting Young People Transitioning from Foster Care: Virginia Findings from National Survey and Policy Scan* by Child Trends for the
Better Housing Coalition and Children’s Home Society of Virginia, Elizabeth Jordan, JD, Garet Fryar, BA, Kerry DeVooght, MSW, 58% foster care kids graduate high school by 19 compared to the general population of 87%. <3% graduate college by 25 compared to 28%. 46% are employed by 26 compared to 80%. 51% are eligible for employer-provided health insurance compared to 71%. Only 9% have their own residence by age 26 compared to 30% of the general population in Virginia. For youth involved in foster care, 42% females and 68% males will be arrested by age 26 whereas only 5% females and 22% males of the general population. Virginia has 14%-22% of its foster care youth between ages 16-20 which according to Child Trends is the transition age. 


**Foster Care Transitional Aged Youth in Loudoun County** 
According to the *The Adoption and Foster Care Analysis and Reporting System*, in 2020 there were 48 children in foster care in only Loudoun County which was .8% in the state of Virginia. As you can see in the pie chart above, over 2/3 of those children were boys and 1/3 were girls and the minority of them of ethnicity of Hispanic. Almost 50% of those children were white, 25% black and less than 5% Asian and multi-racial. When we are looking at only transitional aged youth from 18-24 where 21 years old is the average time a foster child ages out, there were only 8 children. In Loudoun County, it does not seem like there are many foster care youths who are aging out of the system but only 9 other counties have greater than 9 foster care kids over the age of 18. 



```{r}

## not sure if this is relevant 
library(readxl)
outcomes_2020 <- read_excel("01-Doc/Summaries/data/outcomes-2020.xlsx")
View(outcomes_2020)

```



**Income and Household** 

```{r}
## JaiDa needs to add her information here 
```

