---
title: "Loudoun_County_Juvenile-Detention"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

                                Kyle Jacobs 

                           Virginia State University 
 
                                  DSPG


Youth incarceration is a major issue in Virginia. The public pattern of youth imprisonment declining  65% in the U.S. since 2003, youth imprisonment has been declining in Virginia. Youth impressment started to decline in  2003. Virginia Spends  $171,588 per incarcerated youth annually (DJJ 2016). For every 15$ the DJJ spends only 14 gets allocated to community based services. more than 92% of youth who entered Virginia youth detainment facilities showed symptoms of Attention Deficit Hyperactivity Disorder (ADHD), Conduct Disorder (CD), Oppositional Defiant Disorder (ODD), Substance Abuse, or Substance Dependence; conceded to youth penitentiaries in 2016 were mediated on a crime offense, 7 of every 10 of which were offenses against an individual (Virginia Department of Juvenile Justice (DJJ), Data Resource Guide Fiscal Year 2016 (Richmond: Virginia DJJ, 2016). Over 90% of the DJJ budget was spent on incarcerated youth while 2% was spent on community.  



 








```{201_DSPG_Loudoun.Rproj}
summary(cars)
```

## Including Plots



```{r pressure, echo=FALSE}
plot(pressure)
```

