---
title: "Artical Summary"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

(Article 1)

Prevalence of co-occurring disorders among juveniles committed to detention centers


Bibliography: The Practical Adolescent Diagnostic Interview (PADDI), an organized analytic meeting intended to assemble essential data about substance use problems, emotional wellness conditions, and related encounters, was utilized in routine assessment of all teenagers focused on two adolescent detainment habitats. Unknown information from 252 continuously conceded young people were investigated to survey the predominance and seriousness of trouble spots and to give a primer investigation of interrelationships among those issues. Results showed that a greater part of teenagers showed numerous issues. While predominance rates were high across sexual orientation, females showed fundamentally more prominent emotional wellness issues and abuse narratives.

Reference

Abrantes, A. M., Hoffmann, N. G., & Anton, R. (2005). Prevalence of co-occurring disorders among juveniles committed to detention centers. International journal of offender therapy and comparative criminology, 49(2), 179–193. https://doi.org/10.1177/0306624X04269673

(Article 2)

Mapping the social service pathways of youth to and through the juvenile justice system: A comprehensive review

Bibliography: .Adolescent Crime is anything but a sound quality for any non-industrial nation and unquestionably not for a broadly refined and crowded nation like India. India has been experiencing overpopulation and low proficiency for a long time now and it influences the development of the country. Training is the way to improve the condition of the country and more adolescent wrongdoing, youngsters get lesser quality schooling and it continues to pull down the country. Not just that, it likewise harms the future and isn't sound for the fate of the country.

Reference 

Maschi, T., Hatcher, S. S., Schwalbe, C. S., &amp; Rosato, N. S. (2008, April 23). Mapping the social service pathways of youth to and through the juvenile justice system: A comprehensive review. Children and Youth Services Review. https://www.sciencedirect.com/science/article/pii/S0190740908001059. 


(Article 3)

Prediction of Juvenile Delinquencies in Correlation with Education


Bibliography: The reason for this survey was to detail the human or social assistance needs and administration use designs (i.e., medical care, instruction, social administrations, kid government assistance, psychological wellness, and substance misuse) that impact youth '''s entrance and delayed association with the adolescent equity framework. What rose up out of the writing was an example of administration needs and earlier help that put youth in danger of adolescent equity contribution.

Reference

R. Akila, J. BrindhaMerin, R. K. Vishal and V. Krishnan S.H., "Prediction of Juvenile Delinquencies in Correlation with Education," 2020 6th International Conference on Advanced Computing and Communication Systems (ICACCS), 2020, pp. 987-993, doi: 10.1109/ICACCS48705.2020.9074338.


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
