---
title: "Loudoun_County_Juvenile-Detention"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

                                Kyle Jacobs 

                           Virginia State University 
 
                                  DSPG


Youth incarceration is a major issue in Virginia. The public pattern of youth imprisonment declining  65% in the U.S. since 2003, youth imprisonment has been declining in Virginia. Youth impressment started to decline in  2003. Virginia Spends  $171,588 per incarcerated youth annually (DJJ 2016). For every 15$ the DJJ spends only 14 gets allocated to community based services. more than 92% of youth who entered Virginia youth detainment facilities showed symptoms of Attention Deficit Hyperactivity Disorder (ADHD), Conduct Disorder (CD), Oppositional Defiant Disorder (ODD), Substance Abuse, or Substance Dependence; conceded to youth penitentiaries in 2016 were mediated on a crime offense, 7 of every 10 of which were offenses against an individual (Virginia Department of Juvenile Justice (DJJ), Data Resource Guide Fiscal Year 2016 (Richmond: Virginia DJJ, 2016). Over 90% of the DJJ budget was spent on incarcerated youth while 2% was spent on community.  




(Article 1)

"Prevalence of co-occurring disorders among juveniles committed to detention centers"
output: html_document


bibliography: The Practical Adolescent Diagnostic Interview (PADDI), an organized analytic meeting intended to assemble essential data about substance use problems, emotional wellness conditions, and related encounters, was utilized in routine assessment of all teenagers focused on two adolescent detainment habitats. Unknown information from 252 continuously conceded young people were investigated to survey the predominance and seriousness of trouble spots and to give a primer investigation of interrelationships among those issues. Results showed that a greater part of teenagers showed numerous issues. While predominance rates were high across sexual orientation, females showed fundamentally more prominent emotional wellness issues and abuse narratives.


Refrence

Abrantes, A. M., Hoffmann, N. G., & Anton, R. (2005). Prevalence of co-occurring disorders among juveniles committed to detention centers. International journal of offender therapy and comparative criminology, 49(2), 179–193. https://doi.org/10.1177/0306624X04269673

(Article 2)

"Mapping the social service pathways of youth to and through the juvenile justice system: A comprehensive review"


output: html_document
bibliography: .Adolescent Crime is anything but a sound quality for any non-industrial nation and unquestionably not for a broadly refined and crowded nation like India. India has been experiencing overpopulation and low proficiency for a long time now and it influences the development of the country. Training is the way to improve the condition of the country and more adolescent wrongdoing, youngsters get lesser quality schooling and it continues to pull down the country. Not just that, it likewise harms the future and isn't sound for the fate of the country.

Refrence 

Maschi, T., Hatcher, S. S., Schwalbe, C. S., &amp; Rosato, N. S. (2008, April 23). Mapping the social service pathways of youth to and through the juvenile justice system: A comprehensive review. Children and Youth Services Review. https://www.sciencedirect.com/science/article/pii/S0190740908001059. 


(Article 3)

title: "Prediction of Juvenile Delinquencies in Correlation with Education"
output: html_document 

Bibiliogrphy: The reason for this survey was to detail the human or social assistance needs and administration use designs (i.e., medical care, instruction, social administrations, kid government assistance, psychological wellness, and substance misuse) that impact youth '''s entrance and delayed association with the adolescent equity framework. What rose up out of the writing was an example of administration needs and earlier help use that put youth in danger of adolescent equity contribution.

Refrence

R. Akila, J. BrindhaMerin, R. K. Vishal and V. Krishnan S.H., "Prediction of Juvenile Delinquencies in Correlation with Education," 2020 6th International Conference on Advanced Computing and Communication Systems (ICACCS), 2020, pp. 987-993, doi: 10.1109/ICACCS48705.2020.9074338.








```{201_DSPG_Loudoun.Rproj}
summary(cars)
```

## Including Plots



```{r pressure, echo=FALSE}
plot(pressure)
```

