---
title: "serving"
author: "Rebstock"
date: "7/13/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Local Bus 2018-2023 
https://www.loudoun.gov/DocumentCenter/View/122385/TDP-2018-2028-?bidId=
https://www.loudoun.gov/3444/Transit-Development-Plan

* Serves 3 shopping centers 
*  Start point is a stop in the Shenandoah Square shopping center north of the County offices
(Shenandoah Building) and adjacent to Mail Stop
*  The route has never charged a fare. The Town of Leesburg contributes a portion of the
cost to fund the service

```{r}
# number of riders monthly for weekdays, saturday, sunday 
mar15 <- c(1148, 228, 210)
# average of riders for weekday, sat, sun 
averg <- c(52, 57, 42)

```



OAR 2020 
https://oarnova.org/accountability/financial-documents 
2020 report 
https://www.oarnova.org/images/FY_2020_AR.pdf 
```{r}
# 2020 
1 <- 180
c <- 3355
m <- .75
f <- .23
undisclosed <- .2 

tay <- .3 
no_high <- .17 
college <- .11 

#2019 
l <- 221
c <- 4757
m <- .72
f <- .27

tay <- .36 
no_high <- .15 
college <- .11 

#2018
l <- 142
c <- 3917
m <- .76
f <- .24

tay <- .36 
no_high <- .15 
 
#2017
l <- 159
c <- 3413
m <- .75
f <- .24

tay <- .31 
no_high <- .19 


```


Oxford House for all Virginia Houses November 2019 -2020 
https://oxfordhouse.org/userfiles/file/evaluations.php
https://oxfordhouse.org/userfiles/file/doc/eval_va2020.pdf 

They take 17-74 ages, NO time limit as long as they stay sober 

```{r}


average_stay <- 9 #months 
median_stay <- 5 
prior_home <- 61.3 #percent 
prior_jail <- 79.6
edu <- 12.1 #years '


```




Medicaid (all of VA) july 2021
Monthly enrollments 
https://www.dmas.virginia.gov/media/3619/dmas-enrollment-report-july-2021.pdf
https://www.dmas.virginia.gov/media/3503/medicaid-expansion-infographic.pdf
https://www.dmas.virginia.gov/data/ 

WIOA Monthly reports 2020
https://vcwnorthern.com/program-reports/

Affordable Dwelling Unit Program 2020
Monthly reports on how many ADU are sold and rented out and a waitlist number 
https://www.loudoun.gov/431/Affordable-Dwelling-Unit-Advisory-Board 

Continum of Care Homeless Shelters in Northern VA 202-2021
file:///Users/julierebstock/Downloads/2021_PIT_Combined1.pdf

553 single adults who were formerly in foster care are homeless (pg44) 

2017-10
2018-7
2019-20
2020-22
2021-12

page 46 
21% of total homeless in Loudoun are 18-24 


Good Shepherd Alliance 
https://goodshepherdalliance.org/how-we-serve/
3000+ are helped each year 
10000+ beds 
77% go on to stable housing following 


Adult Literacy Program Loudoun
https://loudounliteracy.org/wp-content/uploads/2020/11/Annual-Report-FY20.pdf 

```{r}


classroom <- 396
tutoring <- 20
jobsite <- 49 
ged <- 2 
workforce <- 105 

served <- 543 
hispanic <- 58
asian <- 24
white <- 10
other <- 6 


```












